---
title: "CLT_WUP"
author: "Chris Gonzalez"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
 

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```



```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k3 = x.avg


p <- ggplot(my1000, aes(x=k3),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k3)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k3),' sd = ',sd(my1000$k3)))

```


The dataset with numb = 9 consists of 9 samples, where each value is the square root of 3. Applying the central limit theorem, the standard deviation of the dataset decreases to 14.098 from the original value of 41.68. As the sample size increases, the standard deviation is expected to continue decreasing, in line with the central limit theorem. This reduction in standard deviation signifies a narrower spread of the sample means and a more precise estimation of the population mean.The mean should stay the simlar to the orginal.  What we actually got for the standard deviation is `r sd (my1000$k3)`. I expect the numbers to continue to lower.


```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k3)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))
```
Indeed, as expected, when using numb = 16, which corresponds to the square root of 4, the standard deviation is lower compared to the previous case. The reduction in standard deviation suggests that the distribution of the sample means is becoming more concentrated around the population mean. Specifically, since the original standard deviation was 41.68, observing a decrease to approximately one-fourth of that value indicates a substantial decrease in variability and an improvement in the precision of estimating the population mean. This trend aligns with the central limit theorem, which predicts a decrease in standard deviation as the sample size increases. We got `r sd(my1000$k4)`


```{r}
numb = 25
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k5 = x.avg


p <- ggplot(my1000, aes(x=k5),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k5)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k5),' sd = ',sd(my1000$k5)))
```
The central limit theorem continues to hold true as the sample size increases. For numb =25, the standard deviation is `r sd(my1000$k5)`, which can be calculated using the provided data. This value demonstrates the decreasing trend of standard deviation as the sample size grows. The decrease in standard deviation signifies the increasing precision in estimating the population mean as the sample size becomes larger, aligning with the expectations set by the central limit theorem.

```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k6 = x.avg


p <- ggplot(my1000, aes(x=k6),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k6)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k6),' sd = ',sd(my1000$k6)))
```

In conclusion, the application of the central limit theorem is evident as the sample size increases. With numb = 36, we observe that the standard deviation, calculated as `r sd(my1000$k6)`, is even lower compared to previous cases. This decreasing trend in the standard deviation further confirms the central limit theorem's prediction. The continuous reduction in standard deviation signifies a higher precision in estimating the population mean as the sample size grows. Thus, the central limit theorem holds true, as evidenced by the decreasing standard deviation observed with numb = 36.














